### 2019-10-23 paper/4_simulation.tex
Paraphrase chap 1

@@

We are ready to verify theoretical bound of DS by numerical experiments.
DS is a convex optimization program, and there are many library devoted on that.
We choose the Python Library CVXPY.
But we will not implement that here.

@@

Each data point is repeated for 32 times, and taken average.
We plot the absolute log error
\PF {h'-ABS;h,h}
\DispN {
\NC \eta_{\Rm{abs}}
=\NC \RB {\log_2 {\VNm {\V {h} -\Hat {\V {h}}}_2}} _{\Ss{avg}}, \NR
}
and relative log error.
\PF {h'-REL;h,h}
\DispN {
\NC \eta_{\Rm{rel}}
=\NC \F {\RB {\log_2 {\VNm {\V {h} -\Hat {\V {h}}}_2}} _{\Ss{avg}}}
{\RB {\log_2 {\VNm {\V {h}}_2}} _{\Ss{avg}}} \NR
}
The averaged error values are plotted along with the theoretical expected error of DS, derived in chap.\ 3, namely
\PF {h'-TH;5,2}
\DispN {
\NC \eta_{\Rm{th}}
=\NC \F{5}{2} + \log \RB{L N_H} + \log \log N_H \NR
}

@@

@@

Reasonably, for all methods, a higher \m {\s} corresponds to higher \eta_{\Rm{rel}} and \eta_{\Rm{rel}}.
The trends of absolute and relative error are the same, and in the below we call them simply error.

@@

The function being minimized is \m {\VNm {\V {g}}_1}.
Let \m {\V {g} _0} denote the starting value of \m {\V {g}}, and \m {\V {g} ^{\star}} the the point of convergence.
Then \cite [BoV04] (p.505, eq.9.56) gives a bound of the number of iteration of Newton method.
If just take that as the complexity bound for DS, it becomes
\PF {cc-DS;cc-0,g-0}
\DispN {
\NC C_{\Rm{DS}}
= \NC C_0 \VNm {\V {g}_0 -\V {g} ^{\star}}_1
+ \log_2 \log_2 \F {1} {\e} \NR
}
where \m {C_0} is constant related to implementation of Newton method, and \m {\e} the tolerance of error.
According to the analysis of \cite [BoV04] (eq.9.57), for most cases \m {-\log_2 \log_2 \e} can be bounded by \m {6}.
Also, \m {C_0} usually assumes the value of about several hundred;
They gives an example \m {C_0 =375} (with their notation, \m {C_0 =\dfrac {20 -8\a} {\a \b \RB {1 -2\a}^2}}, where \m {\a = 0.1, \b = 0.8, \e =0.01}, and \m {\a, \b} are parameters used in the Backtrack Line Tracing algorithm).

Since we are doing big-O analysis, we feel that we have more license on making approximation.
For concreteness, we may assume that we start the iteration by specifying the Least Square estimator as the initial value of \m {\V {g}_0}, namely
\PF {g-0;g-LS,pp}
\Disp {
\NC \V {g}_0
=\NC \V {g}_{\Rm {LS}} \NR
\NC = \NC \RB {\M {P} ^\Adj \M {P}} ^{-1} \M {P} ^\Adj \V {y} \NR
}
If we drop it, we may write the complexity of DS to be, simply,
\PF {cc-DS;oo,g,g}
\Disp {
\NC C_{\Rm{DS}}
=\NC \MC {O} \SB {\VNm {\V {g}_{\Rm {LS}} -\V {g} ^\star} _1} \NR
}
For simplicity we assume
\DispN {
\PF {g;g,}
\NC \V {g} ^\star
\approx \NC \V {g} \NR
}
Indeed, this is the main objective of our investigation!
And by restricted isometry, \m {\M {P}} has unity-normed, almost orthogonal columns, so
\DispN {
\PF {pp,pp;ii-nn-hh-2}
\NC \M {P} ^\Adj \M {P}
\approx \NC I _{N_{H}^2} \NR
}
Thus
\Disp {
\PF {cc;oo;g,pp}
\NC C_{\Rm{DS}}
=\NC \MC {O} \SB {
   \VNm {\V {g} +\RB {\M {P} ^\Adj \M {P}} ^{-1} \M {P} ^\Adj \V {z}
   -\V {g}} _1} \NR
\NC =\NC \MC {O} \SB {\VNm {\M {P} ^\Adj \V {z}} _1} \NR
}
\m {\RB {\M {P} ^\Adj \V {z}} \DB {j}} Complex Normal distribution, and is easily bounded by \m {\s}.
\Disp {
\PF {;oo,nn-hh-2}
\NC =\NC \MC {O} \SB {N_{H}^2 \s} \NR
}

On the other hand, Tropp and Gilbert \cite [TrG07b] discussed the complexity of OMP, and they give
\PF {cc-OMP;oo,nn-hh-2}
\Disp {
\NC C_{\Rm{OMP}}
=\NC \MC {O} \SB {N_H^2 \log N_Y} \NR
}
And it would appear that this is greater than \m {C_{\Rm{DS}}}.
However, we dropped some constants in analyzing \m {C_{\Rm{DS}}}, and here \m {\log N_Y} is really small in our case.
If we drop it, then we get \m {\MC {O} \SB {N_H^2}} again.

At least our discussion suggests that, approximately
\PF {cc-OMP;cc-DS}
\Disp {
\NC C_{\Rm{OMP}}
\approx \NC C_{\Rm{DS}} \NR
\NC \approx \NC \MC {O} \SB {N_H^2} \NR
}

>>>>

We are ready to verify theoretical bound of DS by numerical experiments.
DS is a convex optimization program, and there are many library devoted on that.
For present purpose, we choose the ready-made Python library CVXPY.
For the implementation details, see Diamond and Boyd \cite [DiB16]

However, it turns out direct implementation of () exhibit extraordinarily large complexity, and we would like to recast the problem in a more tractable form.
Towards that end, we found out that Candès and Romberg \cite [CaR05] has shown that DS can be simplified as an linear program (LP).
However, the situation is more cubersome than that, since they deal with real vectors, but we consider the complex ones.
Fortunately, they have briefly pointed out, complex DS can be recast as an second-order cone program (SOCP), and SOCP is one of the several standard convex programming problems for which there are already numerous efficient algorithms.

Before describing the recast, for ease of treatment we would like to represent complex vector and matrices by real, extended vectors and matrices.
\Result
{Definition}
{
For \m {\V {x} \in \MB {C} ^{M}}, define the real representation \m {\MC {R} \SB {\V {x}}} of \m {\V {x}} to be
%
\Disp {
\NC \MC {R} \SB {\V {x}}
\in \NC \MB {R} ^{2M} \NR
\NC \MC {R} \SB {\V {x}} _{\SB {m}}
= \NC \startcases
\NC \MF {Re} \SB {\V {x} _{\SB {m'}}}, \MC m =2m' \NR
\NC \MF {Im} \SB {\V {x} _{\SB {m'}}}, \MC m =2m'+1 \NR
\stopcases \NR
\NC m' 
= \NC  0, 1, 2, \ldots, M-1 \NR
}
%
The injectivity is obvious, and we may define \m {\MC {R} ^{-1}} so that
%
\Disp {
\NC \MC {R} ^{-1} \SB {\MC {R} \SB {\V {x}}}
=\NC \V {x} \NR
}
}
%
Accordingly, the following generalization to complex matrices is valid, once we call the ring representation of complex numbers.
\Result
{Definition}
{
For \m {\M {A} \in \MB {C} ^{M_1 \D M_2}}, define real representation \m {\MC {R} \SB {\M {A}}} of \m {\M {A}} to be
%
\Disp {
\NC \MC {R} \SB {\M {A}}
\in \NC \MB {R} ^{2M_1 \D 2M_2} \NR
\NC \MC {R} \SB {\M {A}} _{\SB {m_1,m_2}} =
\NC \startcases
\NC \MF {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC (m_1, m_2) = (2m_1', 2m_2') \NR
\NC \MF {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC (m_1, m_2) = (2m_1'+1, 2m_2') \NR
\NC -\MF {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC (m_1, m_2) = (2m_1', 2m_2'+1) \NR
\NC \MF {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC (m_1, m_2) = (2m_1'+1, 2m_2'+1) \NR
\stopcases \NR
\NC m_1 
= \NC 0, 1, 2, \ldots, M_1 -1 \NR
\NC m_2 
= \NC 0, 1, 2, \ldots, M_2 -1 \NR
}
}

With these, we define
%
\Disp {
\NC \T {\V {y}}
= \NC \MC {R} \SB {\V {y}}
\in \MB {R} ^{2N_y} \NR
%
\NC \T {\V {g}}
= \NC \MC {R} \SB {\V {g}}
\in \MB {R} ^{2N_h} \NR
%
\NC \T {\M {P}}
= \NC \MC {R} \SB {\M {P}}
\in \MB {R} ^{2N_y \D 2N_h} \NR
%
\NC \T {\M {P}} ^\Adj
= \NC \MC {R} \SB {\M {P} ^\Adj}
\in \MB {R} ^{2N_y \D 2N_h} \NR
%
\NC \T {\V {z}}
= \NC \MC {R} \SB {\V {z}}
\in \MB {R} ^{2N_y} \NR
}
%
such that, by construction,
%
\Disp {
\NC \V {\T {y}}
= \NC \M {\T {P}} \V {\T {g}} +\V {\T {z}} \NR
}

Furthermore, introduce the following matrices to identify the components where we want to take \m {\ell_2}-norm, in the manner similar to an indicator function.
%
\Disp {
\NC {\V {u}}_{n_h}
\in \NC \MB {R} ^{N_h} \NR
\NC \RB {\V {u}_{n_h}} _{\SB {n_h'}}
= \NC
\startcases
1, \Q \MC n_h' =n_h \NR
0, \Q \NC \Rm {otherwise} \NR
\stopcases \NR
\NC \T {\M {U}}_{n_h} \in \NC \MB {R} ^{2N_h \D 2N_h} \NR
\NC \RB {\T {\M {U}}_{n_h}} _{\SB {n_h', n_h''}}
= \NC
\startcases
1, \Q \MC n_h' =2n_h,\; n_h'' =2n_h \NR
1, \Q \MC n_h' =2n_h +1,\; n_h'' =2n_h +1 \NR
0, \Q \NC \Rm {otherwise} \NR
\stopcases \NR
\NC n_h, n_h', n_h'' 
= \NC 0, 1, 2, \ldots, N_h -1 \NR
}
%
And denote \m {\V {1}} to be the all-\m{1} vector for short, and \m {\V {0}} the all-\m{0} vector, whose dimension will be specified from context.
Now, if we introduce vector \m{\V {m}}
%
\Disp{
\NC \V {m} \in \NC \MB {R} ^{N_h} \NR
\NC \V {m} \DB{n_h}
= \NC \Nm{\V {g} \DB{n_h}} \NR
\NC n_h, n_h', n_h'' 
= \NC 0, 1, 2, \ldots, N_h -1 \NR
}
%
to denote the entrywise complex modulus of \m{\V {g}}, we see that the convex optimization now takes the form
%
\Disp {
\NC \Hat {\T {\V {g}}}
= \NC \startcases
\NC \Min {\T {\V {g}}', \V {m}} \Q
\MC \IP { \V {1}, \V {m} } \NR
\NC \Rm {subject} \; \Rm {to} \Q
\MC \VNm { \T {\M {U}}_{n_h} \T {\V {g}}' }_2
\leq \IP { \V {u}_{n_h}, \V {m} } \NR
\NC \MC \VNm { \T {\M {U}}_{n_h} \T {\M {P}}^\Adj \RB { \T {\M {P}} \T {\V {g}}' -\T {\V {y}} } }_2
\leq \g \NR
\stopcases \NR
\NC n_h 
= \NC 0, 1, 2, \ldots, N_h-1 \NR
}

\startsection [title={Second Order Cone Programming}]

We shall see furthermore that the program can be cast into an SOCP.
To make the point clearer, we rewrite Program () into an extended block matrix form, by defining auxiliary variables as follows,
%
\Disp{
\NC \V {t}
= \NC \startTheMatrix
\NC \V {0} \NR
\NC \V {1} \NR
\stopTheMatrix
\in \MB {R} ^{3N_h} \NR
%
\NC \V {x}'
= \NC \startTheMatrix
\NC \T {\V {g}}' \NR
\NC \V {m} \NR
\stopTheMatrix
\in \MB {R} ^{3N_h} \NR
}
%
with
%
\Disp{
\NC \M {A}_i
= \NC \startTheMatrix
\NC \T {\M {U}}_{i}, \NC \M {0} \NR
\stopTheMatrix
\in \MB {R} ^{2N_h \D 3N_h} \NR
%
\NC \V {b}_i
= \NC \V {0}
\in \MB {R} ^{2N_h} \NR
%
\NC \V {c}_i
= \NC \startTheMatrix
\NC \V {0} \NR
\NC \V {u}_{i} \NR
\stopTheMatrix
\in \MB {R} ^{3N_h} \NR
%
\NC d_i
= \NC 0 \NR
%
\NC i 
= \NC 0, 1, 2, \ldots, N_h -1 \NR
}

And
%
\Disp{
\NC \M {A}_i
= \NC \startTheMatrix
\NC -\T {\M {U}}_{i -N_h} \T {\M {P}}^\Adj \T {\M {P}}, \NC \M {0} \NR
\stopTheMatrix
\in \MB {R} ^{2N_h \D 3N_h} \NR
%
\NC \V {b}_i
=\NC \T {\M {U}}_{i -N_h} \T {\M {P}}^\Adj \T {\V {y}}
\in \MB {R} ^{2N_h} \NR
%
\NC \V {c}_i
= \NC \V {0}
\in \MB {R} ^{3N_h} \NR
%
\NC d_i
= \NC \g \NR
%
\NC i 
= \NC N_h, N_h +1, N_h +2, \ldots, 2N_h -1 \NR
}
%
The step that we convert \m {\Hat {\V {g}}} back is same as Algorithm () is same as before, but this is listed for sake of completeness.

\Result
{Algorithm}
{
\startitemize[n]
\item Input \m{\M {P} \in \MB {C} ^{N_y \D N_h}}, \m{\V {y} \in \MB {C} ^{N_y}}, \m{\g > 0}.
\item Define \m{\V {t}, \V {x}, \M {A}_i, \V {b}_i, \V {c}_i, d_i} according to ().
\item Calculate
%
\Disp{
\NC \Hat {\V {x}}
\LA \NC \startcases
\NC \Min {\V {x}' \in \MB {C} ^{N_h}}
\MC \IP {\V {t}, \V {x}'} \NR
\NC \Rm {subject} \; \Rm {to}
\Q  \MC \VNm {\M {A} _{i} \V {x}' +\V {b} _{i}} _2
\leq \IP {\V {c}_{i}, \V {x}'} +\V {d}_i \NR
\NC \MC i 
=0, 1, 2, \ldots, 2N_h -1 \NR
\stopcases \NR
}
\item Extract
%
\Disp{
\NC \Hat{\T{\V {g}}}
\LA \NC \Hat{\V {x}} _{\SB {0 : 2N_h-1}} \NR
}
\item Convert 
%
\Disp{
\NC \Hat{\V {g}}
\LA \NC \MC{R} ^{-1} \SB {\Hat{\T{\V {g}}}} \NR
}
\item Calculate
%
\Disp {
\NC \Hat {G}
\LA \NC \Rm {vec}^{-1} \SB {\Hat {g}} \NR
}
\item Calculate
%
\Disp {
\NC \Hat {\M {H}}
\LA \NC \M {K} \Hat {\M {G}} \M {K}^\Adj \NR
}
\item Output \m {\Hat {\M {H}}}.
\stopitemize
}

@@

@@

@@

Each data point is repeated for 32 times, and taken average.
We plot the absolute log error
%
\DispNum {e',s;lo,vg} {
\NC \e_{\Rm{abs}}
=\NC \RB {\log_2 {\VNm {\V {h} -\Hat {\V {h}}}_2}} _{\Ss{avg}}, \NR
}
%
and relative log error.
%
\DispNum {e',l;lo,vg} {
\NC \e_{\Rm{rel}}
=\NC \F {\RB {\log_2 {\VNm {\V {h} -\Hat {\V {h}}}_2}} _{\Ss{avg}}}
{\RB {\log_2 {\VNm {\V {h}}_2}} _{\Ss{avg}}} \NR
}
%
The averaged error values are plotted along with the theoretical expected error of DS, derived in chap.\ 3, namely
%
\DispNum {e',h;52,NH} {
\NC \e_{\Rm{th}}
=\NC \F{5}{2} + \log \RB{L N_H} + \log \log N_H \NR
}

@@

Reasonably, for all methods, a higher \m {\s} corresponds to higher \m {\eta_{\Rm{rel}}} and \m {\eta_{\Rm{rel}}}.
The trends of absolute and relative error are the same, and in the below we call them simply error.

@@

The function being minimized is \m {\VNm {\V {g}}_1}.
Let \m {\V {g} _0} denote the starting value of \m {\V {g}}, and \m {\V {g} ^{\star}} the the point of convergence.
Then \cite [BoV04] (p.505, eq.9.56) gives a bound of the number of iteration of Newton method.
If just take that as the complexity bound for DS, it becomes
%
\DispNum {C,S;C0,1e'} {
\NC C_{\Rm{DS}}
= \NC C_0 \VNm {\V {g}_0 -\V {g} ^{\star}}_1
+ \log_2 \log_2 \F {1} {\e} \NR
}
%
where \m {C_0} is constant related to implementation of Newton method, and \m {\e} the tolerance of error.
According to the analysis of \cite [BoV04] (eq.9.57), for most cases \m {-\log_2 \log_2 \e} can be bounded by \m {6}.
Also, \m {C_0} usually assumes the value of about several hundred;
They gives an example \m {C_0 =375} (with their notation, \m {C_0 =\dfrac {20 -8\a} {\a \b \RB {1 -2\a}^2}}, where \m {\a = 0.1, \b = 0.8, \e =0.01}, and \m {\a, \b} are parameters used in the Backtrack Line Tracing algorithm).

Since we are doing big-O analysis, we feel that we have more license on making approximation.
For concreteness, we may assume that we start the iteration by specifying the Least Square estimator as the initial value of \m {\V {g}_0}, namely
%
\DispNum {g,0;gL,Py} {
\NC \V {g}_0
=\NC \V {g}_{\Rm {LS}} \NR
\NC = \NC \RB {\M {P} ^\Adj \M {P}} ^{-1} \M {P} ^\Adj \V {y} \NR
}
%
If we drop it, we may write the complexity of DS to be, simply,
%
\DispNum {C,S;Og,g1} {
\NC C_{\Rm{DS}}
=\NC \MC {O} \SB {\VNm {\V {g}_{\Rm {LS}} -\V {g} ^\star} _1} \NR
}
%
For simplicity we assume
%
\DispNum {g-;g-,-g} {
\NC \V {g} ^\star
\approx \NC \V {g} \NR
}
%
Indeed, this is the main objective of our investigation!
And by restricted isometry, \m {\M {P}} has unity-normed, almost orthogonal columns, so
%
\DispNum {P,P;IN,H2} {
\NC \M {P} ^\Adj \M {P}
\approx \NC I _{N_{H}^2} \NR
}
%
Thus
%
\Disp {
\NC C_{\Rm{DS}}
=\NC \MC {O} \SB {
   \VNm {\V {g} +\RB {\M {P} ^\Adj \M {P}} ^{-1} \M {P} ^\Adj \V {z}
   -\V {g}} _1} \NR
\NC =\NC \MC {O} \SB {\VNm {\M {P} ^\Adj \V {z}} _1} \NR
}

If we agree that, for high probability,
%
\Disp {
\NC \MC {O} \RB {\VNm {\M {P} ^\Adj \V {z}} _{\SB {j}}}
= \NC \s \MC {O} \RB {1} \NR
}

By condition (), it is easy to see that \m {\RB {\M {P} ^\Adj \V {z}} _{\SB {j}}} observes Complex Standard Normal distribution.
and is easily bounded by \m {\s}.
%
\DispNum {--;ON,2s} {
\NC C_{\Rm{DS}}
=\NC \MC {O} \SB {N_{H}^2 \s} \NR
}

On the other hand, Tropp and Gilbert \cite [TrG07a] discussed the complexity of OMP, and the proof of technical lemmata in it can be found in the companion paper \cite [TrG07b].
They give
%
\DispNum {C,O;ON,NY} {
\NC C_{\Rm{OMP}}
=\NC \MC {O} \SB {N_H^2 \log N_Y} \NR
}
%
And it would appear that this is greater than \m {C_{\Rm{DS}}}.
However, \m {\log N_Y} is really small in our experiments.
and we dropped some constants, too, in analyzing \m {C_{\Rm{DS}}}.
If we drop \m {\log N_Y}, then we get \m {\MC {O} \SB {N_H^2}} again.

In summary
%
\DispNum {C,P;CD,H2} {
\NC C_{\Rm{OMP}}
\approx \NC C_{\Rm{DS}} \NR
\NC \approx \NC \s \MC {O} \SB {N_H^2} \NR
}

### 2019-10-23 paper/5_conclusion.tex
Paraphrase chap 1

Moreover, assuming the virtual channel model according to uniform linear array response, we managed to prove explicitly, following the spirit of Cand\`es and Tao (2007), that the probability that the expected square error is bounded is overwhelming.
We thus have derived a probability bound of performance on a fairly general setting, where the bounding constant is expressed as an explicit function of physical parameters, such as the number of path.

Afterwards we transformed DS into an SOCP, which is quite different as in the original DS (where we have an LP instead).
Simulation is done, and DS's performance is compared to OMP.
\color[red]{(To be done)}

>>>>

Moreover, assuming the virtual channel model according to uniform linear array response, we managed to prove explicitly, following the spirit of Cand\`es and Tao \cite [CaT07], that the probability that the expected square error is bounded is overwhelming.
We thus have derived a probability bound of performance on a fairly general setting, where the bounding constant is expressed as an explicit function of physical parameters, such as the number of path.

Afterwards we transformed DS into an SOCP, which is quite different as in the original DS (where we have an LP instead).
Simulation is done, and DS's performance is compared to OMP.
DS is slightly but steadily more accurate than OMP, while DS exhibits rather high complexity.

### 2019-10-23 paper/abstract.tex
Delete conversion from complex to real DS
Paraphrase chap 1

Multiple-input-multiple-output (MIMO) is widely expected to be used in the next-generation wireless communication.
However, reliable communication in such r\`egime often desires that the channel state information be known at the receiver, necessary for example in beamforming algorithm and channel calibration, but it is usually not easy to estimate real-world wireless channel.

Meanwhile, the millimeter wave channel, which is usually used in tandem with MIMO, often exhibits sparse properties, if the sparsity is exploited, few observations may suffice to estimate the channel.
Such algorithm falls under the study of Compressive Sensing, an active area that has recently emerged.
A promiment estimator is The Dantzig Selector (DS) proposed by Tao and Cand\'es, and it is DS which was first applied in channel estimation context, and as originally perceived, it ideal in certain senses.
However, Orthogonal Matching Pursuit (OMP) later emerges as a solution with lower complexity, and following-up literature, as a result, usually used OMP rather than DS.
In this article, we consider a hybrid structure at both the transmitter and receiver end, each of them having both digital and analog percoders and combiners.
We argue in favor of DS, since DS encompasses a more general setting than OMP, such as in its requirement of restricted isometry property (RIP) only, as well as in its tolerance of noise corruption.
Indeed, we shall refine Tao and Cand\'es's bound, and generalize under current settings, thus giving a viable solution for the estimation of millimeter wave channel.
Moreover, we show explicitly that DS may be cast as a second order cone problem (SOCP), and primal-dual technique is ready to be used.
Simulation is done with both DS and OMP, and we discuss their respective merits as our conclusion.

>>>>

Multiple-input-multiple-output (MIMO) is expected to be the next-generation technology for wireless communication.
However, for MIMO system it is not easy to estimate the channel, while reliable communication often requires that the channel state information be known at the receiver, necessary e.g.\ in beamforming and channel calibration.
Meanwhile, the millimeter wave (mm-Wave) band, often used in MIMO context, is known to exhibit sparsity, and emerging work on compressive sensing suggests that if sparsity is exploited, fewer measurement suffices to estimate the channel.
Dantzig Selector (DS), proposed by Tao and Cand\'es, has been introduced early in channel estimation literature.
But Orthogonal Matching Pursuit (OMP) emerges, and having a lower complexity, it ends up being popular.
In this paper, we consider a mm-Wave MIMO channel, and a hybrid structure at both the transmitter and receiver end.
Using pilot signal and designed random beamformer, we employ DS to estimate the channel, arguing in favor of its greater generality, its tolerance of noise corruption, and its lower averaged error, despite of having greater complexity.
We then proved a bound for the expected square error of DS, as well as bounded probability of success, showing explicit dependency on the number of path and channel sparsity.
DS can be cast as a second order cone problem (SOCP), so that feasible code for convex programming may be applied.
Simulation is done on DS and other methods, and we discuss their respective merits.

### 2019-10-23 paper/notation.tex
Use BibTeX, conform to IEEE citation style
Paraphrase chap 1

\starttable[|l|l|l|] \HL
\NC Expression \VL Meaning or Definition \VL More Explanation \SR \HL
\NC \m {\RB {x+1} \RB {x+2}} \VL round parentheses \VL used only for precedence \AR \HL
\NC \m {f \SB {x}} \VL square brackets \VL used only for arguments or parameter \AR \HL
\NC \m {\CB {2, 3, 5, 7}} \VL curly braces \VL used only for sets \AR \HL
\NC \m {\V {v} \DB {3}} \VL double square brackets \VL used only for entry indices \AR \HL
\NC \m {\Nm {a}} \VL magnitude \VL for real or complex numbers \AR \HL
\NC \m {\MF {Re} \SB {a}} \VL real part \VL for complex numbers \AR \HL
\NC \m {\MF {Im} \SB {a}} \VL imaginary part \VL for complex numbers \AR \HL
\NC \m {\V {a}} \VL vector \VL  \AR \HL
\NC \m {\M {A}} \VL matrix \VL  \AR \HL
\NC \m {\V {1}} \VL all-1 vector \VL dimension will be clear from context \AR \HL
\NC \m {\V {0}} \VL all-0 vector \VL dimension will be clear from context \AR \HL
\NC \m {\V {a} \DB {n}} \VL \m {n}-th component of \m {\V {a}} \VL  \AR \HL
\NC \m {\M {A} \DB {m,n}} \VL \m {m,n}-th entry of \m {\M {A}} \VL  \AR \HL
\NC \m {\MB {K}} \VL either \m {\MB {R}} or \m {\MB {C}} \VL  \AR \HL
\NC \m {\MB {V}_{\MB {K}} \SB {N}} \VL Hilbert space \m {\MB {K}^N} over \m {\MB {K}} \VL  \AR \HL
\NC \m {\MB {M}_{\MB {K}} \SB {M,N}} \VL collection of \m {M} by \m {N} matrices \VL  \AR \HL
\NC \m {\V {a} \DB {0}} \VL the first component of \m {\V {a}} \VL  \AR \HL
\NC \m {\M {A} \DB {0,0}} \VL the upper-left entry of \m {\V {A}} \VL  \AR \HL
\NC \m {m\; \Rm{Mod}\; n} \VL remainder of \m {m} divided by \m {n} \VL with \m {m, n \geq 0} and \m {0 \leq m\; \Rm{Mod}\; n <n} \AR \HL
\NC \m {\VNm {\V {a}} _p} \VL \m {\ell_p}-norm of \m {\V {a}} \VL \m {p >0} \AR \HL
\NC \m {\VNm {\V {a}} _\infty} \VL the maximum-magnitude \VL  \AR
\NC  \VL component of \m {\V {a}} \VL  \AR \HL
\NC \m {\MB {P} \SB {A}} \VL probability of \m {A} \VL  \AR \HL
\NC \m {\MB {E} \SB {X}} \VL expectation of \m {X} \VL  \AR \HL
\NC \m {\Ss {Var} \SB {X}} \VL variance of \m {X} \VL  \AR \HL
\stoptable

>>>>

\starttable[|l|l|l|] \HL
\NC Expression \VL Meaning or Definition \VL More Explanation \SR \HL
\NC \m {\RB {x+1} \RB {x+2}} \VL round parentheses \VL used only for precedence \AR \HL
\NC \m {f \SB {x}} \VL square brackets \VL used only for arguments or parameter \AR \HL
\NC \m {\CB {2, 3, 5, 7}} \VL curly braces \VL used only for sets \AR \HL
\NC \m {\Nm {a}} \VL magnitude \VL for real or complex numbers \AR \HL
\NC \m {\MF {Re} \SB {a}} \VL real part \VL for complex numbers \AR \HL
\NC \m {\MF {Im} \SB {a}} \VL imaginary part \VL for complex numbers \AR \HL
\NC \m {\V {a}} \VL vector \VL \AR \HL
\NC \m {\M {A}} \VL matrix \VL \AR \HL
\NC \m {\V {1}} \VL all-1 vector \VL dimension will be clear from context \AR \HL
\NC \m {\V {0}} \VL all-0 vector \VL dimension will be clear from context \AR \HL
\NC \m {\V {a} _{\SB {n}}} \VL \m {n}-th component of \m {\V {a}} \VL \AR \HL
\NC \m {\M {A} _{\SB {m,n}}} \VL \m {m,n}-th entry of \m {\M {A}} \VL \AR \HL
\NC \m {\V {a} _{\SB {0}}} \VL the first component of \m {\V {a}} \VL  \AR \HL
\NC \m {\M {A} _{\SB {0,0}}} \VL the upper-left entry of \m {\V {A}} \VL  \AR \HL
\NC \m {\MB {K}} \VL either \m {\MB {R}} or \m {\MB {C}} \VL  \AR \HL
\NC \m {\MB {K} ^{N}} \VL Hilbert space \m {\MB {K}^N} over \m {\MB {K}} \VL  \AR \HL
\NC \m {\MB {K} ^{M \D N}} \VL collection of \m {M} by \m {N} matrices \VL  \AR \HL
\NC \m {m\; \Rm {Mod}\; n} \VL remainder of \m {m} divided by \m {n} \VL with \m {m, n \geq 0} and \m {0 \leq m\; \Rm {Mod}\; n <n} \AR \HL
\NC \m {\VNm {\V {a}} _p} \VL \m {\ell_p}-norm of \m {\V {a}} \VL \m {p >0} \AR \HL
\NC \m {\VNm {\V {a}} _\infty} \VL the maximum-magnitude \VL  \AR
\NC  \VL component of \m {\V {a}} \VL  \AR \HL
\NC \m {\MB {P} \SB {A}} \VL probability of event \m {A} \VL  \AR \HL
\NC \m {\MB {E} \SB {X}} \VL expectation of random variable \m {X} \VL  \AR \HL
\NC \m {\Ss {Var} \SB {X}} \VL variance of random variable \m {X} \VL  \AR \HL
\stoptable
